Simulation

### 2023-10-31 simulation.qmd
Sample from cmdstanr model

```{r}
#' Simulate ar(1) data
#' 
#' Adapted from <https://experienced-sampler.netlify.app/post/stan-hierarchical-ar/#testing>
#'
#' @param I number of individuals
#' @param t number of time points per individual
#' @param sigma residual standard deviation of observations
#' @param alpha_hat intercept mean
#' @param alpha_scale intercept standard deviation
#' @param beta_hat ar(1) slope mean
#' @param beta_scale ar(1) slope standard deviation
#'
#' @return a list of variables to send to Stan
#'
#' @examples simulate()
simulate <- function(
    I = 30, 
    t = 10, 
    sigma = 1, 
    alpha_hat = 4, 
    alpha_scale = 1, 
    beta_hat = 0.4, 
    beta_scale = 0.1
) {

@@

```{r}
fit <- cmdstanr::cmdstan_model("model-ar1.stan", compile = FALSE)
fit$format(
  canonicalize = list("deprecations"), 
  overwrite_file = TRUE, 
  backup = FALSE
)
```

>>>>

```{r}
#' Simulate ar(1) data
#' 
#' Adapted from <https://experienced-sampler.netlify.app/post/stan-hierarchical-ar/#testing>
#'
#' @param I number of individuals
#' @param t number of time points per individual
#' @param sigma residual standard deviation of observations
#' @param alpha_hat intercept mean
#' @param alpha_scale intercept standard deviation
#' @param beta_hat ar(1) slope mean
#' @param beta_scale ar(1) slope standard deviation
#'
#' @return a list of variables to send to Stan
#'
#' @examples simulate()
simulate <- function(
    I = 100, 
    t = 50, 
    sigma = 1, 
    alpha_hat = 4, 
    alpha_scale = 1, 
    beta_hat = 0.4, 
    beta_scale = 0.1
) {

@@

```{r}
model <- cmdstanr::cmdstan_model("model-ar1.stan", compile = FALSE)
model$format(
  canonicalize = list("deprecations"), 
  overwrite_file = TRUE, 
  backup = FALSE
)
model$compile()
fit <- model$sample(
  data = dat, 
  adapt_delta = 0.99
)
```

```{r}
as_draws_df(fit)
```
